I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-08 Paper/Paper_noProof.tex
Writing

In this subsection, we will introduce the method to choose open nodes for MILP model by considering compensating pairs.

@@

We explain the framework in 4 subsections: precomputation, process for one image, process for one node, and global process.

@@

The test neural network is MNIST fully-connected $6\times 100$, and the test image is the image 59 in the standard MNIST image database. This image can have more unstable nodes in each layer.

@@

@@

>>>>

In this subsection, we will introduce the method to choose open nodes for MILP model based on compensating pairs.

@@

We explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.

@@

The test neural network is MNIST fully-connected $6\times 100$, and the test image is the image 59 in the MNIST image dataset.

@@

\[
\begin{array}{c|c|c}

	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
	0  &  2.22 & 2.22  \\ \hline
	10  &  1.84 & 2.03  \\ \hline
	20  &  1.50 & 1.82  \\ \hline
	30  &  1.28 & 1.62  \\ \hline
	40  &  1.14 & 1.44  \\ \hline
	50  &  1.06 & 1.23  \\ \hline
\end{array}
\]

@@

\[
\begin{array}{c|c|c}

	\text{Number of open nodes}  &  \text{Compensating} & \text{Random}  \\ \hline
	0  &  1.758 & 1.758  \\ \hline
	10  &  1.677 & 1.695  \\ \hline
	20  &  1.539 & 1.622  \\ \hline
	30  &  1.431 & 1.542  \\ \hline
	40  &  1.329 & 1.47  \\ \hline
	50  &  1.243 & 1.39  \\ \hline
\end{array}
\]
